An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/motiv.tex
better motiv

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
A configuration error reported recently made MySQL
daemon fail to start~\cite{syserror}.
One entry in a MySQL configuration file is written as 
{\tt datadir=/root/appfinder/mysql}, and the type as well as 
format seem to be correct.
However, the problem is this directory should not be
initiated as a root directory, and the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called system environment-related configuration error.
Both \app and EnCore can handle system execution related
misconfiguration problems.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.

>>>>

\para{Other errors.}
\app can also deal with the configuration errors that can be detected by
existing work, such as EnCore~\cite{zhang14encore} and
CODE~\cite{yuan11context}.
A configuration error reported recently made the MySQL
daemon fail to start~\cite{syserror}.
One entry was written as 
{\tt datadir=/root/appfinder/mysql}, and the type, as well as 
format, seemed correct.
However, the problem is that this directory should not 
contain the root directory; the correct entry
should be {\tt datadir=/appfinder/mysql}.
Such an error is called a system environment-related configuration error.
Both \app and EnCore can handle misconfigurations concerning system execution.
Furthermore, \app is also able to detect type errors and syntax errors
in configuration files.
